### 2023-01-04 cv/cv-body.tex
Fix CV formatting

\hypertarget{peer-reviewed-reports}{%
\section{Peer-reviewed reports}\label{peer-reviewed-reports}}

2022 Grandin, C.J., \textbf{S.C. Anderson}, P.A. English. Arrowtooth
Flounder (\emph{Atheresthes stomias}) Stock Assessment for the West
Coast of British Columbia in 2021. Accepted DFO Can. Sci. Advis. Sec.
Res. Doc.

2022 DFO. A data synopsis for British Columbia groundfish: 2021 data
update. DFO Can. Sci. Advis. Sec. Sci. Resp. 2022/020.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2022/2022_020-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2022/2022_020-fra.html}{French
version}).

\begin{description}
\tightlist
\item[2021]
DFO. Status Update of Pacifc Cod (\emph{Gadus macrocephalus}) for West
Coast Vancouver Island (Area 3CD), and Hecate Strait and Queen Charlotte
Sound (Area 5ABCD) in 2020. DFO Can. Sci. Advis. Sec. Sci. Resp.
2021/002.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-fra.html}{French
version}).
\item[2021]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia. DFO
Can. Sci. Advis. Sec. Res. Doc. 2021/007.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{Research
Document}).
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2021/2021_002-eng.html}{Associated
Science Advisory Report}.
\item[2021]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockfish (\emph{Sebastes ruberrimus}) in British
Columbia. DFO Can. Sci. Advis. Sec. Res. Doc. 2021/008.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_008-eng.html}{Research
Document}).
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}

\hypertarget{dfo-technical-reports}{%
\section{DFO Technical Reports}\label{dfo-technical-reports}}

>>>>

\hypertarget{peer-reviewed-government-reports}{%
\section{Peer-reviewed government
reports}\label{peer-reviewed-government-reports}}

\begin{description}
\tightlist
\item[2022]
Grandin, C.J., \textbf{S.C. Anderson}, P.A. English. Arrowtooth Flounder
(\emph{Atheresthes stomias}) Stock Assessment for the West Coast of
British Columbia in 2021. Accepted DFO Can. Sci. Advis. Sec. Res. Doc.
\item[2022]
DFO. A data synopsis for British Columbia groundfish: 2021 data update.
DFO Can. Sci. Advis. Sec. Sci. Resp. 2022/020.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2022/2022_020-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ScR-RS/2022/2022_020-fra.html}{French
version}).
\item[2021]
DFO. Status Update of Pacifc Cod (\emph{Gadus macrocephalus}) for West
Coast Vancouver Island (Area 3CD), and Hecate Strait and Queen Charlotte
Sound (Area 5ABCD) in 2020. DFO Can. Sci. Advis. Sec. Sci. Resp.
2021/002.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-fra.html}{French
version}).
\item[2021]
\textbf{Anderson, S.C.}, R.E. Forrest, Q.C. Huynh, E.A. Keppel. A
management procedure framework for groundﬁsh in British Columbia. DFO
Can. Sci. Advis. Sec. Res. Doc. 2021/007.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_007-eng.html}{Research
Document},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/SAR-AS/2021/2021_002-eng.html}{Associated
Science Advisory Report}).
\item[2021]
Haggarty D.R., Q.C. Huynh, R.E. Forrest, \textbf{S.C. Anderson}, M.J.
Bresch, E.A. Keppel. Evaluation of potential rebuilding strategies for
Inside Yelloweye Rockfish (\emph{Sebastes ruberrimus}) in British
Columbia. DFO Can. Sci. Advis. Sec. Res. Doc. 2021/008.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2021/2021_008-eng.html}{Research
Document}).
\item[2020]
Forrest, R.E., \textbf{S.C. Anderson}, C.J. Grandin, P.J. Starr.
Assessment of Pacific Cod (\emph{Gadus macrocephalus}) for Hecate Strait
and Queen Charlotte Sound (Area 5ABCD), and West Coast Vancouver Island
(Area 3CD) in 2018. DFO Can. Sci. Advis. Sec. Res. Doc. 2020/070 iv +
204 p.
(\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-eng.html}{English
version},
\href{https://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2020/2020_070-fra.html}{French
version}).
\item[2019]
\textbf{Anderson, S.C.}, E.A. Keppel, A.M. Edwards, 2019. A reproducible
data synopsis for over 100 species of British Columbia groundfish. DFO
Can. Sci. Advis. Sec. Res. Doc. 2019/041. vii + 321 p.
(\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-eng.html}{English
version},
\href{http://www.dfo-mpo.gc.ca/csas-sccs/Publications/ResDocs-DocRech/2019/2019_041-fra.html}{French
version}).
\end{description}

\hypertarget{government-technical-reports}{%
\section{Government Technical
Reports}\label{government-technical-reports}}
